### 2009-04-06 talk/icooolps2009-dotnet/intro.tex
turn arigo into a footnote

The \emph{PyPy} project\footnote{\texttt{http://codespeak.net/pypy/}}
\cite{RigoPedroni06} was initially conceived to develop an implementation of Python which
could be easily portable and extensible without renouncing efficiency.
To achieve these aims, the PyPy implementation is based on a highly
modular design which allows high-level aspects
to be separated from lower-level implementation details.
The abstract semantics of Python is defined by an interpreter written
in a high-level language, called RPython \cite{AACM-DLS07}, which is in fact a subset of
Python where some dynamic features have been sacrificed to allow an
efficient translation of the interpreter to low-level code.
\arigo{But note that it's a full Python interpreter; RPython is only the
language in which this interpreter is written.}

>>>>

The \emph{PyPy} project\footnote{\texttt{http://codespeak.net/pypy/}}
\cite{RigoPedroni06} was initially conceived to develop an implementation of Python which
could be easily portable and extensible without renouncing efficiency.
To achieve these aims, the PyPy implementation is based on a highly
modular design which allows high-level aspects
to be separated from lower-level implementation details.
The abstract semantics of Python is defined by an interpreter written
in a high-level language, called RPython \cite{AACM-DLS07}, which is in fact a subset of
Python where some dynamic features have been sacrificed to allow an
efficient translation of the interpreter to low-level code\footnote{But note that it's a full Python interpreter; RPython is only the
language in which this interpreter is written.}.
